Reliable error estimation for Sobol' indices\thanks{This work is supported by the CITiES project funded by the Agence Nationale de la Recherche (grant ANR-12-MONU-0020) and by the United States National Science Foundation (grant DMS-1522687).}

### 2017-02-19 article_review/Manuscript.tex
More changes

As shown in \cite[Sec. 3]{HicJim}, the group structure of digital nets guarantees the property below affecting any Walsh basis function $\varphi_{\vk}(\vx)=\e^{2 \pi \sqrt{-1} \ip{\vk}{\vx}}$,
\begin{equation}\label{basis_integ_prop}
\frac{1}{b^m}\sum_{\vx\in\mathcal{P}_m}\varphi_{\vk}(\vx)=
\begin{cases}
1,\quad \vk\in\mathcal{P}_m^\perp, \\
0,\quad \vk\notin\mathcal{P}_m^\perp.
\end{cases}
\end{equation}
Therefore, using the Walsh decomposition of $f\in \mathbb{L}^2([0,1]^d)$: \[
f(\vx)=\sum_{\vk\in\naturals_0^d}\hf_{\vk}\varphi_{\vk}(\vx), \]
and defining the value of the integral,
\[ I = \int_{\cube} f(\vx)\,d\vx,\]
property \eqref{basis_integ_prop} leads to
\begin{align}
\nonumber
\absolute{I - \frac{1}{b^m}\sum_{\vx\in\mathcal{P}_m}f(\vx)} &=
\absolute{\hf_{\vzero} - \frac{1}{b^m}\sum_{\vx\in\mathcal{P}_m}\sum_{\vk\in\naturals_0^d}\hf_{\vk}\varphi_{\vk}(\vx)}, \\
\nonumber
&= \absolute{\sum_{\vk\in\mathcal{P}_m^\perp\setminus\{\vzero\}}\hf_{\vk}} \\
& \leq \sum_{\vk\in\mathcal{P}_m^\perp\setminus\{\vzero\}}\absolute{\hf_{\vk}}. \label{3.1.err_bound}
\end{align}
Based on the size of $\absolute{\hf_{\vk}}$ and the structure of dual nets \eqref{dual_net_structure}, in \cite[Sec. 4.1]{HicJim} we proposed an ordering of the \emph{wavenumbers} $\tilde{\vk}(\cdot):\naturals_0\rightarrow\naturals_0^d$. \comment{This ordering $\tilde{\vk}$ is a one-to-one and onto mapping between $\naturals_0$ and $\naturals_0^d$. Thus, we can identify each $\vk\in\naturals_0^d$ with one $\kappa\in\naturals_0$ such that $\tilde{\vk}(\kappa)=\vk$. This ordering ensures that $\mathcal{P}_m^\perp\setminus\{\vzero\}=\{\tilde{\vk}(\lambda b^m)\}_{\lambda=1}^\infty$. If we identify $\hf_{\kappa}=\hf_{\tilde{\vk}(\kappa)}$, the error bound \eqref{3.1.err_bound} becomes,}
\begin{equation}\label{mapped_error_bound}
\absolute{I - \frac{1}{b^m}\sum_{\vx\in\mathcal{P}_m}f(\vx)} \le \sum_{\lambda=1}^{\infty} \left \lvert \hf_{\lambda b^m}\right \rvert.
\end{equation}
\comment{To use the error bound \eqref{mapped_error_bound} to design and automatic algorithm would require the knowledge of the Walsh coefficients. To avoid this assumption, we will estimate them via the fast transform obtained using the precomputed function values. We will refer to the discrete coefficients as $\tf_{m,\kappa}$,}
\[
\tf_{m,\kappa}=\tf_{m,\tilde{\vk}(\kappa)}=\frac{1}{b^m}\sum_{\vx\in\mathcal{P}_m}f(\vx)\overline{\varphi_{\tilde{\vk}(\kappa)}(\vx)}.
\]
\comment{As shown in \cite[Sec. 3]{HicJim}, the error of estimating the true coefficients using the discrete coefficients can be measured,
\begin{equation}\label{discrite_true_relationship}
\tf_{m,\kappa} = \hf_\kappa + \sum_{\lambda=1}^{\infty} \hf_{\kappa + \lambda b^m}, \qquad \text{ for all } \kappa\in\naturals_0,
\end{equation}
However, since there are at most $b^m$ distinct values of $\tf_{m,\kappa}$, we require some assumptions on the decay rate of $\hf_{\kappa}$ to transform \eqref{mapped_error_bound} into a new error bound in terms of the discrete coefficients.}

@@

@@

We also compare the total number of evaluations of each variant. {\color{purple} (Lolo) Results are averaged over $100$ repetitions by applying different scrambling}. For each repetition, we fix the tolerance $\varepsilon=5.10^{-3}$, set $\ell_*=5$, and $r=4$ (the algorithm starts with $512$ Sobol' points). The algorithm error bound factor described in \eqref{errbd} is set to $\mathfrak{C}(m)=10\times 2^{-m}$.

\comment{For the following examples we do not know the true Walsh coefficients of the integrands. Therefore, we cannot say whether they lie inside the cone defined. }The failure rates $r_{\delta_{\underline{S}_u}}$ and  $r_{\delta_{\overline{S}_u}}$ of each estimate are evaluated over the $100$ repetitions. These rates are the proportion of the repetitions in which the true estimation errors failed to satisfy $\delta_{\underline{S}_u} \leq \varepsilon$ and $\delta_{\underline{S}_u} \leq \varepsilon$. When $\delta_{\underline{S}_u} > \varepsilon$ and $\delta_{\underline{S}_u} > \varepsilon$, we can infer that our algorithm parameters that define the cone are not conservative enough and the integrands fall outside the cone \eqref{conecond}.

@@

Figure \ref{boxplots.gfunc} shows boxplots of the $100$ estimation errors $\delta_{\underline{S}_u}$ obtained with both Variant $A.a$ and Variant $A.b$ for the four inputs $x_3,x_4,x_5,x_6$. The dashed horizontal line marks the tolerance $\varepsilon=5.10^{-3}$.
\begin{figure}[t]
\caption{Boxplots of estimation errors $\delta_{\underline{S}_u}$ for the four inputs $x_3,x_4,x_5,x_6$ obtained with both Variant $A.a$ and Variant $A.b$. The dashed horizontal line marks the tolerance $\varepsilon=5.10^{-3}$.}
\vspace*{0.2cm}
\centering
\includegraphics[width=0.45\textwidth]{sobolg_box.eps}
\label{boxplots.gfunc}
\end{figure}

@@

Variant $A.b$ gives lower estimation errors and fewer failure rates than Variant $A.a$ on the four small first-indices $\underline{S}_3$, $\underline{S}_4,\underline{S}_5$, $\underline{S}_6$ which highlights the performance of ``Correlation 2''. The discrepancy is particularly notable for input $x_3$ where Variant $A.a$ reaches a failure rate of $71\%$ against only $2\%$ for Variant $A.b$. Furthermore, Variant $A.b$ requires less evaluations than Variant $A.a$. The boxplots represented in Figure \ref{boxplots.bratley} emphasize the latter observations.
\begin{figure}[t]
\caption{Boxplots of estimation errors $\delta_{\underline{S}_u}$ for the four inputs $x_3,x_4,x_5,x_6$ obtained with both Variant $A.a$ and Variant $A.b$. The dashed horizontal line marks the tolerance $\varepsilon=5.10^{-3}$.}
\vspace*{0.2cm}
\centering
\includegraphics[width=0.45\textwidth]{bratley_box.eps}
\label{boxplots.bratley}
\end{figure}

>>>>

As shown in \cite[Sec. 3]{HicJim}, the group structure of digital nets guarantees the property below affecting any Walsh basis function $\varphi_{\vk}(\vx)=\e^{2 \pi \sqrt{-1} \ip{\vk}{\vx}}$,
\begin{equation}\label{basis_integ_prop}
\frac{1}{b^m}\sum_{\vx\in\mathcal{P}_m}\varphi_{\vk}(\vx)=
\begin{cases}
1,\quad \vk\in\mathcal{P}_m^\perp, \\
0,\quad \vk\notin\mathcal{P}_m^\perp.
\end{cases}
\end{equation}
Therefore, using the Walsh decomposition of $f\in \mathbb{L}^2([0,1]^d)$: \[
f(\vx)=\sum_{\vk\in\naturals_0^d}\hf_{\vk}\varphi_{\vk}(\vx), \]
and defining the value of the integral,
\[ I = \int_{\cube} f(\vx)\,d\vx,\]
property \eqref{basis_integ_prop} leads to
\begin{align}
\nonumber
\absolute{I - \frac{1}{b^m}\sum_{\vx\in\mathcal{P}_m}f(\vx)} &=
\absolute{\hf_{\vzero} - \frac{1}{b^m}\sum_{\vx\in\mathcal{P}_m}\sum_{\vk\in\naturals_0^d}\hf_{\vk}\varphi_{\vk}(\vx)}, \\
\nonumber
&= \absolute{\sum_{\vk\in\mathcal{P}_m^\perp\setminus\{\vzero\}}\hf_{\vk}} \\
& \leq \sum_{\vk\in\mathcal{P}_m^\perp\setminus\{\vzero\}}\absolute{\hf_{\vk}}. \label{3.1.err_bound}
\end{align}
Based on the size of $\absolute{\hf_{\vk}}$ and the structure of dual nets \eqref{dual_net_structure}, in \cite[Sec. 4.1]{HicJim} we proposed an ordering of the \emph{wavenumbers} $\tilde{\vk}(\cdot):\naturals_0\rightarrow\naturals_0^d$. \comment{This ordering $\tilde{\vk}$ is a one-to-one and onto mapping between $\naturals_0$ and $\naturals_0^d$. Thus, we can identify each $\vk\in\naturals_0^d$ with one $\kappa\in\naturals_0$ such that $\tilde{\vk}(\kappa)=\vk$. The ordering is not unique and one should choose it such that large values of $\kappa$ are mapped to smaller values of $\absolute{\hf_{\tilde{\vk}(\kappa)}}$. It also ensures that $\mathcal{P}_m^\perp\setminus\{\vzero\}=\{\tilde{\vk}(\lambda b^m)\}_{\lambda=1}^\infty$. If we identify $\hf_{\kappa}=\hf_{\tilde{\vk}(\kappa)}$, the error bound \eqref{3.1.err_bound} becomes,}
\begin{equation}\label{mapped_error_bound}
\absolute{I - \frac{1}{b^m}\sum_{\vx\in\mathcal{P}_m}f(\vx)} \le \sum_{\lambda=1}^{\infty} \left \lvert \hf_{\lambda b^m}\right \rvert.
\end{equation}
\comment{To use the error bound \eqref{mapped_error_bound} to design and automatic algorithm would require the knowledge of the Walsh coefficients. To avoid this assumption, we will estimate them via the fast transform obtained using the precomputed function values already used to estimate the mean. We will refer to the discrete coefficients as $\tf_{m,\kappa}$,}
\[
\tf_{m,\kappa}=\tf_{m,\tilde{\vk}(\kappa)}=\frac{1}{b^m}\sum_{\vx\in\mathcal{P}_m}f(\vx)\overline{\varphi_{\tilde{\vk}(\kappa)}(\vx)}.
\]
\comment{As shown in \cite[Sec. 3]{HicJim}, the error of estimating the true coefficients using the discrete coefficients can be measured,
\begin{equation}\label{discrite_true_relationship}
\tf_{m,\kappa} = \hf_\kappa + \sum_{\lambda=1}^{\infty} \hf_{\kappa + \lambda b^m}, \qquad \text{ for all } \kappa\in\naturals_0,
\end{equation}
However, since there are at most $b^m$ distinct values of $\tf_{m,\kappa}$, we require some assumptions on the decay rate of $\hf_{\kappa}$ to transform \eqref{mapped_error_bound} into a new error bound in terms of the discrete coefficients.}

@@

\comment{We assumed that evaluating our model is expensive. Thus, we will focus our cost study on the number of function evaluations needed to estimate the indices. The function evaluations used to estimate the indices are the same as the ones used to compute the discrete Walsh coefficients. The only computation cost that could be expensive is the fast transform algorithm. However, on a regular laptop computing the discrete coefficients of $2^{20}$ points takes around $0.5$ seconds while evaluating these points at an average evaluation time of $1$ microsecond, takes a total of around $1$ second.}

@@

We also compare the total number of evaluations of each variant. {\color{purple} (Lolo) Results are averaged over $100$ repetitions by applying different scrambling}. For each repetition, we fix the tolerance $\varepsilon=5\cdot10^{-3}$, set $\ell_*=5$, and $r=4$ (the algorithm starts with $512$ Sobol' points). The algorithm error bound factor described in \eqref{errbd} is set to $\mathfrak{C}(m)=10\times 2^{-m}$.

\comment{For the examples in this section we do not know the true Walsh coefficients of the integrands. Indeed, since the mapping $\tilde{\vk}$ is chosen heuristically, the cone conditions will also depend on each scrambling. Therefore, we cannot say whether the integrands lie inside the cone. For this reason, we define the failure rates $r_{\delta_{\underline{S}_u}}$ and $r_{\delta_{\overline{S}_u}}$ over the $100$ repetitions. These rates are the proportion of the repetitions in which the true estimation errors failed to satisfy $\delta_{\underline{S}_u} \leq \varepsilon$ and $\delta_{\underline{S}_u} \leq \varepsilon$. When $\delta_{\underline{S}_u} > \varepsilon$ and $\delta_{\underline{S}_u} > \varepsilon$, we can infer that our algorithm parameters that define the cone are not conservative enough and at least one integrand ($I_1$, $I_2$, $I_3$, or $I_4$) falls outside the cone \eqref{conecond}.}

@@

Figure \ref{boxplots.gfunc} shows boxplots of the $100$ estimation errors $\delta_{\underline{S}_u}$ obtained with both Variant $A.a$ and Variant $A.b$ for the four inputs $x_3,x_4,x_5,x_6$. The dashed horizontal line marks the tolerance $\varepsilon=5\cdot 10^{-3}$.
\begin{figure}[t]
\caption{Boxplots of estimation errors $\delta_{\underline{S}_u}$ for the four inputs $x_3,x_4,x_5,x_6$ obtained with both Variant $A.a$ and Variant $A.b$. The dashed horizontal line marks the tolerance $\varepsilon=5\cdot 10^{-3}$.}
\vspace*{0.2cm}
\centering
\includegraphics[width=0.45\textwidth]{sobolg_box.eps}
\label{boxplots.gfunc}
\end{figure}

@@

Variant $A.b$ gives lower estimation errors and fewer failure rates than Variant $A.a$ on the four small first-indices $\underline{S}_3$, $\underline{S}_4,\underline{S}_5$, $\underline{S}_6$ which highlights the performance of ``Correlation 2''. The discrepancy is particularly notable for input $x_3$ where Variant $A.a$ reaches a failure rate of $71\%$ against only $2\%$ for Variant $A.b$. Furthermore, Variant $A.b$ requires less evaluations than Variant $A.a$. The boxplots represented in Figure \ref{boxplots.bratley} emphasize the latter observations.
\begin{figure}[t]
\caption{Boxplots of estimation errors $\delta_{\underline{S}_u}$ for the four inputs $x_3,x_4,x_5,x_6$ obtained with both Variant $A.a$ and Variant $A.b$. The dashed horizontal line marks the tolerance $\varepsilon=5\cdot 10^{-3}$.}
\vspace*{0.2cm}
\centering
\includegraphics[width=0.45\textwidth]{bratley_box.eps}
\label{boxplots.bratley}
\end{figure}

### 2017-02-19 article_review/reviewer_letter.tex
More changes

@@

\answer{End of section 3 and beginning of section 5}
\end{itemize}

>>>>

\answer{The function values used to estimate the Sobol' indices are the same to compute the discrite Walsh coefficients. Thus, there are no additional function evaluations needed to compute $\widetilde{S}_{l,m}$. }

@@

\answer{As the reviewer claims, this is a key point that we revised and explained with more detail. It is really hard to verify whether an integrand satisfies the cone condition. Indeed, because we choose our mapping $\tilde{\vk}$ heuristically, the cone conditions will also depend on the scrambling. At the end of section 3 we cited some data-based necessary conditions that can help identify when integrands are not in the cone. In addition, also at the beginning of section 5, we note that if the error bound is not satisfied it is certain that the integrand is not in the cone.}
\end{itemize}
